---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
**Note**: This R package is not mean to be "serious". It's just for learning purposes.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`agconversions`
========

This is an R package that gives various functions by which to convert agricultural statistics from imperial to metric/SI using `hectares`, `sqmeters`, `mtonnes`, `celcius` and `kgha`

Installation
------------

You can install agconversions from github with:

``` r
# install.packages("devtools")
devtools::install_github("gbraich/agconversions")
```

Example
-------

See the vignette for more extensive use, but here's an example:

```{r}
agconversions::celcius(100)
```


For Developers
--------------

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)
Use the internal `multi` function as the machinery for the front-end functions such as `hectares`, `sqmeters`,`mtonnes`, `celcius` and `kgha`.
