---
title: "Using the `ag conversions` package"
author: "Gurneet Braich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `ag conversions` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to convert agricultural statistics without having to manual change every datapoint or lookup conversion ratios? Checkout the functionality offered by `hectares`, `sqmeters`, `mtonnes`, `celcius` and `kgha` by loading the `agconversions` package! 

```{r}
library(agconversions)
```

Want to get out of the middle ages with acres, pounds and farenheit? Never mess up the temperature or an application rate again. Check out the functions below

```{r}
hectares(100:105)
mtonnes(20000)
sqmeters(5000)
celcius(32:40)
kgha(12.5)
```

`apply`-family friendly, too!

```{r}
my_list <- list(50:60, 32, -10)
## So base-R-boring!
lapply(my_list, function(x) (x-32)*5/9)
## Use celcius instead!
lapply(my_list, celcius)
```

It even comes with the ability to display its output in plot form!

```{r}
hectares(50:60, plot_it=TRUE)
```

How about that!!!
